\bf Focusing on Fast Neural Network Inference

### 2018-05-15 wnmt.2018/wnmt.tex
cast

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. We have identified two areas where typical NMT models differ significantly from other deep-learning models that impact on their inference speed. Firstly, NMT models usually contains a large number of output classes, corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words or sub-words in the target sentence. Target sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for each of these issues which together increase batched inference speed by up to 57\% on modern GPUs without affecting model quality.

@@

>>>>

This paper describe the submissions by members of the University of Edinburgh, Adam Mickiewicz University, Tilde and University of Alicante. We submit two systems based on Amun, the fast inference engine for neural machine translation. We partipated

Through efficient implementation and novel enhancements to the algorithms, our fastest submission is by far the fastest in the shared task. By using more complex models and with model distillation, our other submissions combine the inherent speed of our inference engine with better quality translation.

%The team is composed of members from the University of Edinburgh, Adam Mickiewicz University, Microsoft, Tilde, and the Internation Maritime Organization.

@@

As neural machine translation (NMT) models have become the new state-of-the-art, the challenge is to make their deployment efficient and economical. This is the challenge that this shared task is shining a spotlight on.

It is tempting to use a general purpose deep-learning toolkit such as Tensorflow or Pytorch to train and do the the inference where faster translation could be obtained by tuning parameters within the toolkit, and choosing fast models. We believe this is the approach most other submissions have taken.

We take an opposing approach by using and enhancing a custom inference engine, Amun, which is developed on the premise that fast neural network inference is an issue that deserves dedicated tools which are not compromised by other objectives such as training or support for multiple models. As well as delivering on the useful goal of fast inference, it can serve as a test-bed for novel ideas on neural network inference, and is useful as a means to explore the upper limit of the possible speed for a particular model and hardware.

That is, Amun is an inference-only engine that supports a limited number of NMT models that put fast inference on modern GPU above all other consideration. The consequence of this focused approach can be seen in the results of the shared task ???.

We submitted two systems to this year's shared task for the efficient translation on GPU. Our first submission was tailored to be as fast as possible while being above the baseline BLEU score. Our second submission trade some of the speed of first submission to return good quality translation.

We will describe below our experimental setup as well as the enhancements to Amun that we feel enabled it to achieve its outstanding speed.

Exper

//////////////////////////////////////////////

We have identified two areas where typical NMT models differ significantly from other deep-learning models that impact on their inference speed. Firstly, NMT models usually contains a large number of output classes, corresponding to the output vocabulary. Secondly, rather than a single label, the output from machine translation models is a sequence of class labels that makes up the words or sub-words in the target sentence. Target sentence lengths are unpredictable, leading to inefficiencies during batch processing. We provide solutions for each of these issues which together increase batched inference speed by up to 57\% on modern GPUs without affecting model quality.
